### 2019-04-13 paper/paper.tex
edited and reformatted the npm metadata section

\begin{lstlisting}[caption={A mock simplified \code{npm} metadata file.},captionpos=b,
  label=sampleSimpleMetadata, frame=single, firstline=1][t]
{
  "name": "Lorem Ipsum",
  "versions": {
    "1.0.4": {
      "dependencies": {
        "Adipiscing": "~1.7.0",
        "Elit": "5.1.x"
      },
      "devDependencies": {
        "Sed": "0.9.0",
        "Do": ">=1.3.5 <4.0.0"
      }
    },
    "1.0.5": {
      "dependencies": {
        "Adipiscing": "~1.7.0",
      },
      "devDependencies": {
        "Do": ">=1.3.5 <4.0.0"
      }
    },
    "time": {
      "1.0.4": "2017-09-25T06:39:20.596Z",
      "1.0.5": "2018-05-22T08:35:40.227Z",
      "created": "2015-05-18T03:52:55.192Z"
    }
  }
}
\end{lstlisting}

Metadata for every package is available on the \code{npm} registry\footnote{https://registry.npmjs.org/packageName}. 
This metadata is a JSON file containing some info on licensing, documentation links, maintainers, and crucially for 
our purposes a log of each version of the package since it's creation, labelled using semantic versioning \cite{preston-werner},
and a time field containing the timestamp for each version. Each version in the version field contains various bits of 
version specific information such as authors, maintainers, license used, bugs, and a list of dependencies for that specific
version.\\

We obtained the list of all \code{npm} package names from the \code{npm} registry skimdb\footnote{https://skimdb.npmjs.com/registry/\_all\_docs}, and then %TODO fix this footnote, underscores are cursed
downloaded this metadata for all 797,940 packages on the \code{npm} registry, having found the names of all packages using the \code{npm} registry skimdb
, which we then converted to a somewhat simplified form as in Listing \ref{sampleSimpleMetadata} with just version and dependency information as this is all
we care about for this study. There are two kinds of dependencies in the metadata files, a list of runtime dependencies and \code{devDependencies} used in testing and development.\\

We gathered some information on download counts for \code{npm} packages from the \code{npm} API\footnote{https://api.npmjs.org/downloads/range/2010-01-01:2019-04-01/packageName} 
however we found that the npmjs API seems to no longer have any data on download counts before October 1 2017, and so were unable to collect
historic download counts for \code{npm} as a whole or any specific packages.\\

>>>>

\begin{lstlisting}[caption={A mock simplified \code{npm} metadata file.},captionpos=b,
  label=sampleSimpleMetadata, frame=single, firstline=1]
{
  "name": "Lorem Ipsum",
  "versions": {
    "1.0.4": {
      "dependencies": {
        "Adipiscing": "~1.7.0",
        "Elit": "5.1.x"
      },
      "devDependencies": {
        "Sed": "0.9.0",
        "Do": ">=1.3.5 <4.0.0"
      }
    },
    "1.0.5": {
      "dependencies": {
        "Adipiscing": "~1.7.0",
      },
      "devDependencies": {
        "Do": ">=1.3.5 <4.0.0"
      }
    },
    "time": {
      "1.0.4": "2017-09-25T06:39:20.596Z",
      "1.0.5": "2018-05-22T08:35:40.227Z",
      "created": "2015-05-18T03:52:55.192Z"
    }
  }
}
\end{lstlisting}

Metadata for every package is available on the \code{npm}
registry\footnote{https://registry.npmjs.org/packageName}. 
This metadata is a \code{JSON} file containing info 
on licensing, documentation links, and maintainers, as well as
a log of each version of the package since its creation, which 
for our purposes is the most crucial element.
The version data is labelled using semantic 
versioning \cite{preston-werner} and includes a time field containing 
the timestamp of creation for each version. Each version in the version 
field contains various version specific information such as authors, 
maintainers, the license used, bugs, and a list of dependencies for that specific
version.

We obtained the list of all \code{npm} package names from 
the \code{npm} registry \code{skimdb}\footnote{https://skimdb.npmjs.com/registry/\_all\_docs}. Using these names,
we then downloaded the metadata for each of the 797,940 packages hosted by the
\code{npm} registry and then converted this metadata into a somewhat simplified form 
with just version and dependency information, as seen
in Listing \ref{sampleSimpleMetadata}. There are two kinds of dependencies in the metadata
files: runtime dependencies and \code{devDependencies} used in testing and development.

% We gathered information on download counts for \code{npm} packages from the
% \code{npm} API\footnote{https://api.npmjs.org/downloads/range/2010-01-01:2019-04-01/packageName} 
% however we found that the npm.js API seems to no longer have any data on download counts before October 1 2017, and so were unable to collect
% historic download counts for \code{npm} as a whole or any specific packages.\\
